Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-28 1_manuscript/itt-emotion.tex
Back on track, copied from recovery pdf from 2020 sep 27 20:00

  Japan has been known historically for its hospitality being the highest grade. The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}. With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite{al2015characteristics}. Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures hold different expectations \cite{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context? Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast the satisfaction and dissatisfaction factors of both customer groups using natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups. We define hard attributes as those that are difficult to change by a hotel management without investing in infrastructure or real estate. In contrast, soft attributes are easily modifiable by improvements in management.

@@

  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between cultures. These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction. Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.

@@

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:omotenashi}
    To what degree are Chinese and Western tourists satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service?
    \end{rsq}

@@

    \begin{rsq}
    \label{rsq:omotenashi_both}
    Do Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service?
    \end{rsq}
    \end{subrsq}

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Western and Chinese customers can then have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. These different expectations, in turn, will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.

@@

    % Asians vs. Western behavior
    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This increase resulted in several studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce. One example is \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money. Another is  \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another example is \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

@@

    More recent studies have surfaced as well. A cross-country study \cite{FRANCESCO201924} using posts from U.S.A. citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes. According to their results, it appears that U.S.A. customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes. Another couple of studies \cite{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S. tourists using text mining techniques and more massive datasets, although in a restaurant context.

    These last three articles focus on U.S.A. culture, while our study focuses on Western culture. Another difference with our study is that of the context of the study. The first study \cite{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A. and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing. Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall? Our study measures this at a large scale across different hotels in Japan.

@@

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite{bauer1993changing}, tourist motivation \cite{kim2000}, and closer to our study, satisfaction levels \cite{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924, JIA2020104071, HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its leading rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered as excellent. The number of samples in other text-mining studies is also smaller to ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Sentiment Analysis
    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This method is called sentiment analysis or opinion mining. A precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion. This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.

@@

    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections. We show an example of these dependencies in Figure \ref{fig:depparse}. In this study we use the Stanford NLP Dependency Parser, as described in \cite{chen-EMNLP:2014}. A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}. In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}. In our study, this step was necessary to extract adjective modifiers and their subject. We did that by parsing the entire database, and extracting instances of a few determined dependency codes. One of these dependency codes is ``amod'', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g. A big apple). The other dependency code we used was ``nsubj'', or nominal subject, which is the syntactic subject of a class. We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g. The apple is big). This dependency does not necessarily only include a combination of adjectives and nouns, but it can also be connected with copular verbs, nouns, or other adjectives. For this reason we saw necessary to also perform a Part of Speech (POS) tagging of these clauses.

@@

    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite{powers2011}. The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions. We also performed experiments to choose the best value of the parameter C used in the SVM. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives. However, depending on the data, it can increase false negatives. Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives. SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. Examples of tagged sentences are shown in Table \ref{tab:training_examples}.

@@

    \caption{English and Chinese comparison of the top 10 positive keywords per price range.}

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 3258  & friendly    & 5606  \\ \hline

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 541   & friendly    & 1001  \\ \hline

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 157   & location    & 799   \\  

@@

      \caption{English and Chinese comparison of the top 10 negative keywords per price range.}

@@

  % Please add the following required packages to your document preamble:
  % \usepackage{multirow}
  % \usepackage{graphicx}
  \begin{table}[]
    \centering
    \caption{Determination of hard and soft attributes for Chinese keywords. }
    \label{tab:zh_hard_soft_keywords}
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{|c|l|l|}
      \hline
      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
      \end{tabular}%
      }
  \end{table}

@@

@@

    We also can observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews, while it wasn’t statistically identified as a problem at all for their Chinese counterparts. On the other hand, while it appears in both English and Chinese lists, references to ``shopping'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10
    positive keywords list for English-speakers.

@@

    One factor that both populations have in common is, when perceiving the hotel negatively, ``old'' or ``outdated'', or ``obsolete'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges. This is, however, a hard attribute, and is unlikely to change for most hotels.

@@

    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels. From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms. Other mentions are also big markets nearby, or a big bed. We can observe that across different price ranges, the usage of the word ``big'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels. Inspecting closer by taking random samples of the pairs of ``big space'' or ``large area'', we can see that there are also many references to the public bathing facilities in the hotel. In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called \textit{onsen}. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.

>>>>

  Japan has been known historically for its hospitality being the highest grade. The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}. With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}. Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context? Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast the satisfaction and dissatisfaction factors of both customer groups across several price ranges using machine learning to classify the sentiment of texts, and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups. We define hard attributes as those that are difficult to change by a hotel management without investing in infrastructure or real estate. In contrast, soft attributes are easily modifiable by improvements in management.

@@

  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures. These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction. Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.

@@

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:omotenashi}
    To what degree are Chinese and Western tourists satisfied with Japanese \textit{omotenashi} factors such as staff behavior or service?
    \end{rsq}

@@

    \begin{rsq}
    \label{rsq:omotenashi_both}
    Do Western and Chinese tourists have a different reaction to Japanese \textit{omotenashi} factors such as staff behavior or service?
    \end{rsq}
    \end{subrsq}

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Western and Chinese customers can then have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. These different expectations, in turn, will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.

@@

    % Asians vs. Western behavior
    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.

    Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This increase resulted in several studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce. One example is a study by \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money. Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another study, done by \cite{kim2000}, found that American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

@@

    More recent studies have surfaced as well. A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A. citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes. According to their results, it appears that U.S.A. customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes. Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S. tourists using text mining techniques and more massive datasets, although in a restaurant context.

    These last three articles focus on U.S.A. culture, while our study focuses on Western culture. Another difference with our study is that of the context of the study. The first study \cite[][]{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A. and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing. Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall? Our study measures this at a large scale across different hotels in Japan.

@@

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its leading rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered as excellent. The number of samples in other text-mining studies is also smaller to ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Sentiment Analysis
    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This method is called sentiment analysis or opinion mining. A precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion. This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.

@@

    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections. We show an example of these dependencies in Figure \ref{fig:depparse}. In this study we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}. A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}. In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}. In our study, this step was necessary to extract adjective modifiers and their subject. We did that by parsing the entire database, and extracting instances of a few determined dependency codes. One of these dependency codes is ``amod'', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g. A big apple). The other dependency code we used was ``nsubj'', or nominal subject, which is the syntactic subject of a class. We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g. The apple is big). This dependency does not necessarily only include a combination of adjectives and nouns, but it can also be connected with copular verbs, nouns, or other adjectives. For this reason we saw necessary to also perform a Part of Speech (POS) tagging of these clauses.

@@

    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}. The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions. We also performed experiments to choose the best value of the parameter C used in the SVM. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives. However, depending on the data, it can increase false negatives. Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives. SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. Examples of tagged sentences are shown in Table \ref{tab:training_examples}.

@@

    \caption{English and Chinese comparison of the top 10 positive keywords.}

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline

@@

                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  

@@

      \caption{English and Chinese comparison of the top 10 negative keywords.}

@@

  % Please add the following required packages to your document preamble:
  % \usepackage{multirow}
  % \usepackage{graphicx}
  \begin{table}[]
    \centering
    \caption{Determination of hard and soft attributes for Chinese keywords. }
    \label{tab:zh_hard_soft_keywords}
    \resizebox{0.7\textwidth}{!}{%
    \begin{tabular}{|c|l|l|}
      \hline
      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
      \end{tabular}%
      }
  \end{table}

@@

    \resizebox{0.7\textwidth}{!}{%

@@

    We also can observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews, while it wasn’t statistically identified as a problem at all for their Chinese counterparts. On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.

@@

    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges. This is, however, a hard attribute, and is unlikely to change for most hotels.

@@

    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels. From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms. Other mentions are also big markets nearby, or a big bed. We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels. Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel. We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''. In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
